Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study

### 2022-04-14 paper.tex
update

 An interesting feature found in our simulations is that there are a pair of innermost bubbles\
 (dashed box in the top panel of Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
 extending out from the GC on either side of the thin disk.\
 {\color{blue}
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma\
 and probably not related to the X-ray chimneys \citep{Ponti2019}\
 and radio bubbles \citep{Heywood2019}\
 due to their enormous difference in length (the total major-axis length of the X-ray chimneys
 and radio bubbles is 320 pc and 430 pc, respectively; however, the innermost bubbles
 is up to 4 kpc in length).
 }
 The close-up view (right column in Fig. \ref{fig__profile}) of the vertical profiles\
 and slices (Fig. \ref{fig__innerbubbles})\
 demonstrate that there is a sharp pressure jump at the edge of the innermost bubbles at $z=3.62$ kpc,\
 indicating that the innermost bubbles are an expanding reverse shock.\ %{\color{red} KY: Is it verified that the reverse shock is expanding outward? PH: Yes. I have checked that with multiple slices in different time. The reverse shock is expanding outward.}
 The high-density upstream of the reverse shock requires\
 an even higher density downstream.\
 Continuing outward, there exists a dense shell before the gas density drops to values further downstream.
 %Continuing outward, the higher density must match with low density further downstream;\
 %thus there exists a dense shell.\
 The turbulent plasma is therefore bracketed between the downstream of reverse shock\
 and of the outermost forward shock, thus heating the turbulent plasma up considerably.

@@

%\item The clumpiness of the ISM disk has an insignificant impact on the\
%      overall dynamic of the Galactic bubbles.\
%      The development of the reverse shocks (the innermost bubbles) is always
%      associated with the dense disk,\
%      without the disc, only asymmetric forward shocks exist.
%      {\color{red} KY: I removed the second point about the innermost bubbles for now, because I think the following two points should be separated: (1) inclusion of the disk is critical for forming symmetric Galactic bubbles, (2) we found a pair of innermost bubbles which are reverse shocks (and perhaps comment on their properties and/or observable signatures). PH: done! }
{\color{blue}
\item The development of the expanding forward-reverse shock pair is always associated with\
the dense disk, although the clumpiness of the disk has an insignificant impact on the\
overall dynamic of the Galactic bubbles.
Furthermore, in the absence of the disk, only forward shocks are present,
indicating the inclusion of the disk is critical for forming the innermost bubbles.

\item The forward-reverse shock pair heats the turbulent plasma up considerably ($\sim2$ keV) as the plasma is bracketed between their downstream. There exists a dense shell that fits closely to the reverse shock because the gas is immediately compressed as it passes outward through the reverse shock while coinciding with the low gas density further downstream.
}
\item In the oblique jet scenario, the edge of the eROSITA bubbles is a forward shock,\
      originally driven by oblique bipolar jets emanating from the GC 12.39 Myr ago for a duration of 1.2 Myr\
      and significantly expanded within the stratified atmosphere afterwards.\
      The overall extent of the simulated X-ray bubbles is comparable to that of the eROSITA bubbles, though not as limb-brightened.\
      Future models including shock-accelerated CRs may help to resolve this issue by increasing the compressibility of the fluid and enhancing the thermal Bremsstrahlung emissivity at the edge of the X-ray bubbles.
      %The simulated eROSITA bubbles are not as limb-brightened as the observation.\
      %A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
      %in which CRs could increase the compressibility of the fluid,\
      %resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
\item Followed by the forward shock is a turbulent, hot plasma ($\sim2$ keV) filled with the injected CRs in pressure balance with the shocked medium, which we interpret as the \textit{Fermi} bubbles.\
      The similarity of the morphology, temperature, and gamma-ray spectrum between\
      simulated and observed bubbles suggests that\
      the edge of the \textit{Fermi} bubbles are likely associated with the contact discontinuity between the turbulent, hot plasma and the post-shock medium. The surface of the simulated bubbles is not as smooth as the observed ones; inclusion of magnetic fields in the future may help suppress the instabilities at the bubble surface due to the mangetic draping effect.
\item Assuming a leptonic model with a spatially uniform, power-law CRe spectrum ranging from 0.5 MeV to 562.1 GeV, we showed that the observed gamma-ray and microwave spectra can simultaneously reproduced. The best-fit\
      CRe power-law index is found to be 2.4.
\item The elapsed time of 12.39 Myr required for the simulated bubbles
      to reach the desired morphology
      is ten times longer than the typical synchrotron and IC cooling time scale of
      high energy ($\sim100$ GeV) CRe. Thus, re-acceleration of CRe by shocks or turbulence must be considered
      in this model. Since the forward shock is rather far away from the gamma-ray bubbles, stochastic acceleration of CRs by turbulence appears to be more plausible.\
      We will investigate the competition between stochastic acceleration and radiative cooling
      in a future work.
      %{\color{red} KY: This item is to be modified according to the newly added text in the Discussion section. PH: done!}
\end{itemize}

>>>>

 An interesting feature found in our simulations is that there are a pair of innermost bubbles\
 (dashed box in the top panel of Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
 extending out from the GC on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma\
 and probably not related to the X-ray chimneys \citep{Ponti2019}\
 and radio bubbles \citep{Heywood2019}\
 due to their enormous difference in length (the total major-axis length of the X-ray chimneys
 and radio bubbles is 320 pc and 430 pc, respectively; however, the innermost bubbles
 is up to 4 kpc in length).
 The close-up view (right column in Fig. \ref{fig__profile}) of the vertical profiles\
 and slices (Fig. \ref{fig__innerbubbles})\
 demonstrate that there is a sharp pressure jump at the edge of the innermost bubbles at $z=3.62$ kpc,\
 indicating that the innermost bubbles are an expanding reverse shock.\ %{\color{red} KY: Is it verified that the reverse shock is expanding outward? PH: Yes. I have checked that with multiple slices in different time. The reverse shock is expanding outward.}
 The high-density upstream of the reverse shock requires\
 an even higher density downstream.\
 Continuing outward, there exists a dense shell before the gas density drops to values further downstream.
 %Continuing outward, the higher density must match with low density further downstream;\
 %thus there exists a dense shell.\
 The turbulent plasma is therefore bracketed between the downstream of reverse shock\
 and of the outermost forward shock, thus heating the turbulent plasma up considerably.

@@

%\item The clumpiness of the ISM disk has an insignificant impact on the\
%      overall dynamic of the Galactic bubbles.\
%      The development of the reverse shocks (the innermost bubbles) is always
%      associated with the dense disk,\
%      without the disc, only asymmetric forward shocks exist.
%      {\color{red} KY: I removed the second point about the innermost bubbles for now, because I think the following two points should be separated: (1) inclusion of the disk is critical for forming symmetric Galactic bubbles, (2) we found a pair of innermost bubbles which are reverse shocks (and perhaps comment on their properties and/or observable signatures). PH: done! }
\item The development of the expanding forward-reverse shock pair is always associated with\
the dense disk, although the clumpiness of the disk has an insignificant impact on the\
overall dynamic of the Galactic bubbles.
Furthermore, in the absence of the disk, only forward shocks are present,
indicating the inclusion of the disk is critical for forming the innermost bubbles.

\item The forward-reverse shock pair heats the turbulent plasma up considerably ($\sim2$ keV) as the plasma is bracketed between their downstream. There exists a dense shell that fits closely to the reverse shock because the gas is immediately compressed as it passes outward through the reverse shock while coinciding with the low gas density further downstream.

\item In the oblique jet scenario, the edge of the eROSITA bubbles is a forward shock,\
      originally driven by oblique bipolar jets emanating from the GC 12.39 Myr ago for a duration of 1.2 Myr\
      and significantly expanded within the stratified atmosphere afterwards.\
      The overall extent of the simulated X-ray bubbles is comparable to that of the eROSITA bubbles, though not as limb-brightened.\
      Future models including shock-accelerated CRs may help to resolve this issue by increasing the compressibility of the fluid and enhancing the thermal Bremsstrahlung emissivity at the edge of the X-ray bubbles.
      %The simulated eROSITA bubbles are not as limb-brightened as the observation.\
      %A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
      %in which CRs could increase the compressibility of the fluid,\
      %resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
\item Followed by the forward shock is a turbulent, hot plasma ($\sim2$ keV) filled with the injected CRs in pressure balance with the shocked medium, which we interpret as the \textit{Fermi} bubbles.\
      The similarity of the morphology, temperature, and gamma-ray spectrum between\
      simulated and observed bubbles suggests that\
      the edge of the \textit{Fermi} bubbles are likely associated with the contact discontinuity between the turbulent, hot plasma and the post-shock medium. The surface of the simulated bubbles is not as smooth as the observed ones; inclusion of magnetic fields in the future may help suppress the instabilities at the bubble surface due to the mangetic draping effect.
\item Assuming a leptonic model with a spatially uniform, power-law CRe spectrum ranging from 0.5 MeV to 562.1 GeV, we showed that the observed gamma-ray and microwave spectra can simultaneously reproduced. The best-fit\
      CRe power-law index is found to be 2.4.
\item The elapsed time of 12.39 Myr required for the simulated bubbles
      to reach the desired morphology
      is ten times longer than the typical synchrotron and IC cooling time scale of
      high energy ($\sim100$ GeV) CRe. Thus, re-acceleration of CRe by shocks or turbulence must be considered
      in this model. Since the forward shock is rather far away from the gamma-ray bubbles, stochastic acceleration of CRs by turbulence appears to be more plausible.\
      We will investigate the competition between stochastic acceleration and radiative cooling
      in a future work.
      %{\color{red} KY: This item is to be modified according to the newly added text in the Discussion section. PH: done!}
\end{itemize}
